---
title: "MTurkR code for approving/awarding bonuses"
author: "Molly Offer-Westort"
date: "`r format(Sys.Date())`"
output: github_document
---

## Setup

If starting a new session, set AWS access key and load packages.
```{r files, echo=FALSE}
# AWS credentials file
f <- file.path("~", "Box Sync", "Admin", "Mturk_Credentials", "credentials.csv")
credentials_file <- read.csv(file = f)
# Behavior raw data
f <- file.path("~", "Box Sync", "Research", "Behavior", 
               "Shared_Behavior research MOW", "group-shocks", "fall2017", 
               "MTurk", "Raw_Data", "Group_identity_formation_cleaned.csv")
```

```{r aws}
Sys.setenv(AWS_ACCESS_KEY_ID = credentials_file$Access.Key.Id)
Sys.setenv(AWS_SECRET_ACCESS_KEY = credentials_file$Secret.Access.Key)
```

```{r library}
library(MTurkR)
library(foreign)
library(knitr)
```

```{r not_verbose, echo=FALSE}
# set verbose to FALSE
options(MTurkR.verbose = FALSE)
```

## Approve assignments, award bonuses
```{r approval, eval = FALSE}
workers <- GetAssignments(hit = GetReviewableHITs()[,1]) # get all reviewable HITs
workers <- workers[which(is.na(workers$ApprovalTime)),] # ignore already approved ones
ApproveAssignment(workers$AssignmentId) # approve assignments
```

Match to survey (here, the filepath has already been saved as `f`). 
```{r match, eval = FALSE}
dat <- read.csv(file=f, as.is=TRUE) # survey data
workers$surveycode <- trimws(workers$surveycode, which = "both")
```

Assign bonuses. 
```{r bonus, eval = FALSE}
dat$bonus <- dat$stage1/100 # bonus
dat$contrib_text <- paste0("Thank you for participating in this survey. ",
                           "Your bonus is calculated as follows: Your earnings were ",
                           dat$stage1,
                           " tokens. Each token is worth $0.01. Your bonus is $",
                           dat$stage1/100, ". ")


payout <- merge(workers, dat[, c("bonus", "contrib_text", "confirmation_code")], 
                by.x = "surveycode", 
                by.y = "confirmation_code", all.x=TRUE)

# Bonus workers with valid survey codes
payout <- payout[which(payout$surveycode!=""), ]


# Pay bonus
GrantBonus(workers=payout$WorkerId, assignments=payout$AssignmentId,
           amounts=payout$bonus, reasons=payout$contrib_text)
```

When ready, dispose HITs using `DisposeHIT(hit$HITId)`. Search HITs to confirm that all assignments have been completed/approved. 
```{r dispose, eval = FALSE}
SearchHITs()
```


## Recontact workers for multiple waves

Qualifications can also be assigned to recontact workers. 

Specify the vector of unique IDs to be used for recontacting respondents to the preceding wave(s). Here, if we're recontacting workers from the HITs we can just use `workers$WorkerId`. 

Generate a Qualification Type for the subjects to be recontacted, and assign the qualification type to the relevant workers:

```{r , eval = FALSE}  
recontact_qual <-  
  CreateQualificationType(
    name = "follow-up_recontacts", status = "Active",
    description = "Workers from Prior Wave to be Recontacted",
    keywords = "")

recontact_assign_out <-
  AssignQualification(qual = recontact_qual$QualificationTypeId, 
                      workers = workers$WorkerId)
```

After specifying that workers must have been given this qualification type in MTurk, `MTurkR` can also be used to notify the relevant respondents about the follow-up survey via email:

```{r email, eval = FALSE} 
email.subject <- paste("Example Email Subject here")
email.message <- paste(
  "Hello,", 
  "Example message reminding respondents to the prior wave(s) about the preceding HIT(s), requesting that they participate in the following survey, as well.",
  "Include directions regarding how to find the new HIT using a unique keyword.",
  sep = "\n\n")

recontact_email_out <- ContactWorker(subject = email.subject,
                                     msgs = email.message,
                                     workers = workers$WorkerId,
                                     batch = TRUE)

table(recontact_email_out$Valid)
```

When recontacting workers, save the recontact output (`recontact_assign_out` and `recontact_email_out`in the above example) and email text (`email.subject` and `email.message` in the above example) with other data files.



```{r purl, echo=FALSE, message=FALSE, results='hide', purl=FALSE}
# save R chunks as a separate file
options(knitr.duplicate.label = 'allow')
input  = knitr::current_input()  # filename of input document
output = paste(tools::file_path_sans_ext(input), 'R', sep = '.')
knitr::purl(input,output,quiet=T)
```
