---
title: "MTurkR code for group identification project"
author: "Molly Offer-Westort"
date: "`r format(Sys.Date())`"
output: github_document
---

This is code that is used to run sequential batches of HITs on Amazon Mechanical 
Turk. It is built adapting and extending code from the below MTurkR resources, primarily the MTurkR wiki.

For reference:

- Setting up an Amazon Web Services account: <https://docs.aws.amazon.com/AWSMechTurk/latest/AWSMechanicalTurkGettingStartedGuide/SetUp.html>
- MTurkR wiki: <https://github.com/cloudyr/MTurkR/wiki>
  - To set up MTurkR and get access keys: <https://github.com/cloudyr/MTurkR/wiki/Installation>
  - To circumvent batch pricing: <https://github.com/cloudyr/MTurkR/wiki/Circumventing-Batch-Pricing>
- Streamline Your Mechanical Turk Workflow with MTurkR: <https://www.r-bloggers.com/streamline-your-mechanical-turk-workflow-with-mturkr/>

## Setup
```{r files, echo=FALSE}
# To be used later:
# AWS credentials file
f <- file.path("~", "Box Sync", "Admin", "Mturk_Credentials", "credentials.csv")
credentials_file <- read.csv(file = f)
# MOW worker ID
f <- file.path("~", "Box Sync", "Admin", "Mturk_Credentials", 
               "MOW_workerid.csv")
MOW <- readLines(f)
# Behavior raw data
f <- file.path("~", "Box Sync", "Research", "Behavior", 
               "Shared_Behavior research MOW", "group-shocks", "fall2017", 
               "MTurk", "Raw_Data")
```

Set AWS access key. 
(Mine is stored in a csv file, which I read in and saved as the object 
`credentials_file`.)
```{r aws}
Sys.setenv(AWS_ACCESS_KEY_ID = credentials_file$Access.Key.Id)
Sys.setenv(AWS_SECRET_ACCESS_KEY = credentials_file$Secret.Access.Key)
```

Install (if necessary) and load R packages `MTurkR` and `foreign` (and `knitr` for `purl()` function to extract `R` code. )
```{r install, eval=FALSE}
install.packages("MTurkR")
install.packages("foreign")
install.packages("knitr")
```

```{r library}
library(MTurkR)
library(foreign)
library(knitr)
```

```{r not_verbose, echo=FALSE}
# set verbose to FALSE
options(MTurkR.verbose = FALSE)
```

####Sandbox
While testing, use the sandbox, however, worker-specific code will not work. 
```{r sandbox, eval = FALSE}
options(MTurkR.sandbox = TRUE)
```

#### Assign a qualification to a specific worker

As an example, my workerID is stored in a csv file, which I read in and saved as the value stored in `MOW`.

Create a qualification for just MOW (only need to create this once).
```{r MOW, eval = FALSE}
MOWqual <- CreateQualificationType(paste('Qualification for Worker', MOW),
                                   paste('Temporary Qualification for', MOW),
                                   'Active')
```

If already created qualification for MOW, get it. Qualification IDs can also be searched at: <https://requester.mturk.com/qualification_types> or just `SearchQualificationTypes()`. 
```{r MOWsearch}
MOWqual <- SearchQualificationTypes(paste('Qualification for Worker', MOW))
```
Assign Qualification to MOW only (if not already assigned).
```{r MOWassign}
AssignQualification(MOWqual$QualificationTypeId, MOW)
```
Confirm that it has been assigned. 
```{r MOWcheck}
GetQualificationScore(MOWqual$QualificationTypeId, MOW)$Valid==TRUE
```
Use `RevokeQualification()` or `DisposeQualificationType()` if necessary to 
start fresh.

## Starting a new project

Assign qualification to workers who have completed a similar assignment 
previously. 

Create a new qualification (again, this only needs to be done once). 
```{r block, eval = FALSE}
blockqual <-
  CreateQualificationType(
    name="Qualification to Prevent Retakes",
    description="This qualification is for people who have worked for me on this task before.",
    status = 'Active',
    keywords="Worked for me before",
    auto = FALSE)
```

Or find the qualification ID once it already exists.
```{r blockseach}
blockqual <- SearchQualificationTypes("Qualification to Prevent Retakes")
```

Assign the qualification to any workers who have completed a similar 
assignment previously, if necessary. Here, `WorkerIds` would be a vector of 
worker IDs. 
```{r blockassign, eval = FALSE}
AssignQualification(
  qual = blockqual$QualificationTypeId,
  workers = WorkerIds)
```

#### Set up qualification requirements
```{r requirements}
initial_reqs <- paste0(
  # Worker_Locale == US
  GenerateQualificationRequirement("Locale", "==", "US", preview = TRUE),
  
  # Worker_PercentAssignmentsApproved >= 95
  GenerateQualificationRequirement("Approved", ">=", "95", qual.number = 2),
  
  # Worker_NumberHITsApprove >= 50
  GenerateQualificationRequirement("NumberApproved", ">=", "50", qual.number = 3),
  
  # Any block_qualifications
  GenerateQualificationRequirement(blockqual$QualificationTypeId, "DoesNotExist", "", qual.number = 4)#,
  
  # Leave this in for testing for MOW only
  # GenerateQualificationRequirement(MOWqual$QualificationTypeId, "Exists", "", qual.number = 5)
)
```

Create QualificationType for already completed hit, which blocks past workers
(again, only needs to be created once).
```{r requirements2, eval = FALSE}
qual <- CreateQualificationType("Already completed HIT",
                                "Already completed identical HIT before.",
                                "Active")
```
Find the qualification ID once it already exists. 
```{r requirements3}
qual <- SearchQualificationTypes("Already completed HIT")
```
Generate "DoesNotExist" QualificationRequirement structure for later hits.
```{r requirements4}
later_reqs <- paste0(initial_reqs, 
                   GenerateQualificationRequirement(qual$QualificationTypeId, 
                                                    "DoesNotExist", "", 
                                                    qual.number = 6))
```

####Set HITType parameters
```{r hittypes, eval = FALSE}
total <- 60 # total number of total desired assignments

title <- "5 minute survey, $.50 plus bonus"
description <- "Quick survey. Fun and easy. Payment is auto-approved in 5 days."
reward <- ".50"
duration <- seconds(hours = 1)
auto.approval.delay <- seconds(days = 5)
keywords = "survey, questionnaire"
qual.req = initial_reqs

# create HITType w/o qualification requirement
hittype1 <- RegisterHITType(title = title,
                            description = description,
                            reward = reward, 
                            duration = duration, 
                            auto.approval.delay = auto.approval.delay,
                            keywords = keywords,
                            qual.req = qual.req )

# create HITType with qualification requirement
hittype2 <- RegisterHITType(title = title,
                            description = description,
                            reward = reward, 
                            duration = duration, 
                            auto.approval.delay = auto.approval.delay,
                            keywords = keywords,
                            qual.req = later_reqs )
```

####Create the first HIT. 
The first batch of HITs is assigned using `initial_reqs`; assignment then proceeds iteratively, such that, in each wave, only workers who have *not* completed the HIT can be assigned; this is performed using a repeat loop.

Set a variable to index number of completed assignments.
```{r completed}
completed <- 0
```

Set a list to store assignments into.
```{r allassigns}
allassigns <- list()
```

Set the number of assignments per iteration.
```{r assignmentsPerBatch}
assignmentsPerBatch <- 9
```

HITs can be created with a layoutID, or with an html file. layoutIDs can be 
found using the instructions here: <https://docs.aws.amazon.com/AWSMechTurk/latest/AWSMturkAPI/ApiReference_HITLayoutArticle.html#ApiReference_HITLayoutArticle-creatingHITlayoutId>

```{r layoutid_layout, eval = FALSE}
hit <- CreateHIT(hit.type = hittype1$HITTypeId,
                 assignments = assignmentsPerBatch,
                 expiration = seconds(days = 7),
                 hitlayoutid = layoutid)
```

```{r html_layout, eval = FALSE}
f <- file("advert.html")
a <- GenerateHTMLQuestion(file=f)

hit <- CreateHIT(hit.type = hittype1$HITTypeId,
                 assignments = assignmentsPerBatch, 
                 expiration = seconds(days = 7),
                 question = a$string)
```


For an interactive session, you can hold creation of new HITs until approval. 
```{r function}
fun <- function() {
  ANSWER <- ""
  while( ANSWER!="break" & ANSWER!="continue" ){
    ANSWER <- tolower(readline("Please type 'continue' when you are ready to create a new HIT, or 'break' to stop HIT creation: "))
    if (ANSWER!="break"& ANSWER!="continue") cat("Please re-enter text. \n")
  }
  if (ANSWER == "break") {
    cat("breaking loop. \n")
    break
  }
  if (ANSWER == "continue") cat("Creating new HIT...\n")
}
```

```{r verbose}
# set verbose to TRUE for output
options(MTurkR.verbose = FALSE)
```

```{r loop, eval = FALSE}
# start the loop
repeat {
  # Get the number of available assignments.
  g <- GetHIT(hit$HITId, response.group = "HITAssignmentSummary")$HITs$NumberOfAssignmentsAvailable
  
  # check if all assignmentsPerBatch have been completed
  if (as.numeric(g) == 0) {
    # if yes, retrieve submitted assignments
    w <- length(allassigns) + 1
    allassigns[[w]] <- GetAssignments(hit = hit$HITId)
    
    # assign blocking qualification to workers who completed previous HIT
    AssignQualification(qual$QualificationTypeId, 
                        allassigns[[w]]$WorkerId)
    
    # increment number of completed assignments
    completed <- completed + assignmentsPerBatch
    
    # optionally display total assignments completed thus far
    if (getOption("MTurkR.verbose")) {
      message(paste("Total assignments completed: ", completed, "\n", sep=""))
    }
    
    # check if enough assignments have been completed
    if(completed < total) {
      
      if(interactive()) fun() # check to see if you're ready to create the next hit
      
      # don't create more additional assignments than total
      if(completed + assignmentsPerBatch > total) { 
        assignmentsPerBatch <- total - completed
      }
      
      # if ready, create another HIT
      hit <- CreateHIT(hit.type = hittype2$HITTypeId,
                       assignments = assignmentsPerBatch,
                       expiration = seconds(days = 7),
                       question = a$string)
      
      # wait some time and check again
      Sys.sleep(180)
    } else {
      # if total met, exit loop:
      cat("Total met")
      break
    }
  } else {
    # wait some time and check again
    Sys.sleep(30) # seconds to wait between checking for assignments
  }
}

```
Save all assignments for all HITs as a data.frame. 
```{r save, eval = FALSE}
m <- do.call("rbind", allassigns)
write.csv(m, paste(f, "/MTurkAssignments"))
```
Then, approve HITs. Useful commands if something goes wrong: `ExpireHIT(hit$HITId)`, `DisposeHIT(hit$HITId)`, `SearchHITs()`. 

```{r purl, echo=FALSE, message=FALSE, results='hide', purl=FALSE}
# save R chunks as a separate file
options(knitr.duplicate.label = 'allow')
input  = knitr::current_input()  # filename of input document
output = paste(tools::file_path_sans_ext(input), 'R', sep = '.')
knitr::purl(input,output,quiet=T)
```
